---
title: "Compare Adjusted and Original Qualification Score - Experiment-1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)

source("C://Users//Christian//Documents//GitHub//CausalModel_FaultUnderstanding//data_loaders//load_consent_create_indexes_E1.R")
df_consent <- load_consent_create_indexes();

```

## About this report

1- How adjusted_score and qualification_score are distributed 
2- How many people increased their score relative to their peers? 
3- How many people decreased? 
4- Who were these people who increased and decreased (distribution w.r.t. original score)?

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## #----------------------------------------------------------------
# 1- How adjusted_score and qualification_score are distributed 

```{r density plots, echo=FALSE}


#Center (subtract the mean) and Scales (divided by the standard deviation)
qualification_scores <- scale(df_consent$qualification_score, center=TRUE, scale=TRUE)
irt_scores <- scale(df_consent$adjusted_score, center=TRUE, scale=TRUE)

score_type <- rep("original",length(qualification_scores))
original_score_list <- cbind(qualification_scores,score_type)
score_type <- rep("adjusted",length(irt_scores))
irt_score_list <- cbind(irt_scores,score_type)

all_score_list <- rbind(original_score_list,irt_score_list)
df_all_scores <- data.frame(all_score_list)
colnames(df_all_scores) <- c("score","type")
df_all_scores$score <- as.numeric(as.character(df_all_scores$score))

df_all_scores %>%
  ggplot(aes(x=score, fill=type)) +
  #geom_histogram(binwidth=0.05, color="darkgrey", fill="lightblue") +
  geom_density(alpha=0.3)+
  theme_minimal()+
  theme(
    legend.position=c(0.85, 0.90),
    panel.spacing = unit(0.1, "lines"),
    strip.text.x = element_text(size = 12),
    plot.title = element_text(size=14),
    axis.text.x = element_text(angle = 20, hjust = 1, size=12)
  ) +
  xlab("Scores (centered and scaled)") +
  ylab("Frequency") +
  ggtitle("Qualification score distribution E2") 

```


