---
title: "Compare Adjusted and Original Qualification Score - Experiment-1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)

source("C://Users//Christian//Documents//GitHub//CausalModel_FaultUnderstanding//data_loaders//load_consent_create_indexes_E1.R")
df_consent <- load_consent_create_indexes();

```

### Comparing Adjusted and Original Qualification Score - Experiment-1

The goal of this analysis is to investigate the impact of the score adjustment in computing the association between score and the other covariates, e.g, years of experience, age, gender, explanation size, confidence, and accuracy of tasks.

#### Sections
1. How are the adjusted and original qualification score distributed?
2. How many people had their score increased after adjustment? 
3. How many people had their score decreased? 
4. Are the following covariates better correlated with adjusted score than the origional score?
4.1 Years of programming and Score 
4.2 
4.3 Age and Score 
4.4 Gender and Score
4.4 Explanation size and Score 
4.5 Correlation of Duration of task and Score 
4.5 Correlation of Duration of task and Score 





#### *This is an R Markdown format used for publishing markdown documents to GitHub. When you click the* **Knit** *button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.*

## #----------------------------------------------------------------
# 1- How adjusted_score and qualification_score are distributed 

```{r density plots, echo=FALSE}


#Center (subtract the mean) and Scales (divided by the standard deviation)
qualification_scores <- scale(df_consent$qualification_score, center=TRUE, scale=TRUE)
irt_scores <- scale(df_consent$adjusted_score, center=TRUE, scale=TRUE)

score_type <- rep("original",length(qualification_scores))
original_score_list <- cbind(qualification_scores,score_type)
score_type <- rep("adjusted",length(irt_scores))
irt_score_list <- cbind(irt_scores,score_type)

all_score_list <- rbind(original_score_list,irt_score_list)
df_all_scores <- data.frame(all_score_list)
colnames(df_all_scores) <- c("score","type")
df_all_scores$score <- as.numeric(as.character(df_all_scores$score))

df_all_scores %>%
  ggplot(aes(x=score, fill=type)) +
  #geom_histogram(binwidth=0.05, color="darkgrey", fill="lightblue") +
  geom_density(alpha=0.3)+
  theme_minimal()+
  theme(
    legend.position=c(0.85, 0.90),
    panel.spacing = unit(0.1, "lines"),
    strip.text.x = element_text(size = 12),
    plot.title = element_text(size=14),
    axis.text.x = element_text(angle = 20, hjust = 1, size=12)
  ) +
  xlab("Scores (centered and scaled)") +
  ylab("Frequency") +
  ggtitle("Qualification score distribution E2") 

```

The chart shows that the adjusted score smoothed the distribution,
but still preserved the two general patterns of concentration on 
high and low medium-to-low scores. 

However, it also increased the frequency of the lowest score and
highest score groups. The final distribution has more oa an
exponential shape, while the original one had a right skewed Gaussian
shape.


The reason for the smoothing is two-fold: adjusted score is continuous scale and the original 
shifted some very low scores to a low-to-medium score. The latter
corresponds to giving a lower weight to questions that most people
got it correctly This was the case of question 4.
