---
title: \vspace{3.5in}"Entropy Comparison between Adjusted and Original Qualification Score - Experiment-1"
author: "Christian Medeiros Adriano"
date: "`r Sys.Date()`"
bibliography: "..//..//bibtex//rmd_references.bib"
csl: "..//..//bibtex//acm-sig-proceedings.csl"
output:
   pdf_document:
      fig_caption: true
      number_sections: true
---
\newpage
\tableofcontents 
\listoffigures
\listoftables
\newpage 

    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(entropy)

source("C://Users//Christian//Documents//GitHub//CausalModel_FaultUnderstanding//data_loaders//load_consent_create_indexes_E1.R")
df_consent <- load_consent_create_indexes();

```

# About this report

Compare the dispersion of the adjusted versus the original score. 

# Comparing Distributions

## How does the entropy (spread) of the distributions compare?
### Discretized adjusted_score
Discretization consists of forcing the adjusted_score values to fit the same bins of the qualification_score distribution (5 bins, from zero to four).

```{r compute entropy discretized, echo=FALSE}

#Discretized
qualification_disc <- discretize(df_consent$qualification_score, numBins = 5)
irt_disc <- discretize(df_consent$adjusted_score,numBins = 5)

original_entropy <- entropy(qualification_disc,method = "Jeffreys")
adjusted_entropy <- entropy(irt_disc,method = "Jeffreys")

change =100*((adjusted_entropy-original_entropy)/original_entropy)

print(paste0("Change in entropy= ",round(change,2),"%"))

```

Discretized adjusted_score showed a large drop in entropy. The drop in entropy was unexpected, because the goal of the adjusted score was to re-balance the grades based on the difficulty of questions inferred by the number of people who got each question right.

Note that this discretrized distribution can also be used as a shifted distribution to study model invariance.

## Not discretized, which is how the adjusted_score values will be used.
```{r compute entropy, echo=FALSE}
#Not scaled and Not discretized
original_entropy <- entropy(df_consent$qualification_score,method = "Jeffreys")
adjusted_entropy <- entropy(df_consent$adjusted_score,method = "Jeffreys")
change =100*((adjusted_entropy-original_entropy)/original_entropy)

print(paste0("Change in entropy= ",round(change,2),"%"))
```

However, without discretization, the entropy decreased only 1.04%.

## Comparative Entropy by Participant Group
Was the change in entropy more accentuated for certain groups of participants?



# Comparing Rankings
## Ranking the participants by their score, how many changed their positions? 

## How do participants who increased their ranking position compare to others w.r.t. their years of experience?

## How do participants who decreased their ranking position compare to others w.r.t. their years of experience?

## Are participants who increased, descreased, not changed ranking positions statistically significant distinct w.r.t. to score and years of experience?

# Comparing Correlation
## Years of programming and Score 
## Age and Score 
## Gender and Score

# References

