---
title: \vspace{3.5in}"Entropy Comparison between Adjusted and Original Qualification Score - Experiment-1"
author: "Christian Medeiros Adriano"
date: "`r Sys.Date()`"
bibliography: "..//..//bibtex//rmd_references.bib"
csl: "..//..//bibtex//acm-sig-proceedings.csl"
output:
   pdf_document:
      fig_caption: true
      number_sections: true
---
\newpage
\tableofcontents 
\listoffigures
\listoftables
\newpage 

    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library (entropy)

source("C://Users//Christian//Documents//GitHub//CausalModel_FaultUnderstanding//data_loaders//load_consent_create_indexes_E1.R")
df_consent <- load_consent_create_indexes();

```

# About this report

Compare the dispersion of the adjusted versus the original score. 

# Comparing Distributions


```{r density plots, echo=FALSE}

#Center (subtract the mean) and Scales (divided by the standard deviation)
qualification_scores <- scale(df_consent$qualification_score, center=TRUE, scale=TRUE)
irt_scores <- scale(df_consent$adjusted_score, center=TRUE, scale=TRUE)

```

## How does the entropy (spread) of the distributions compare?


# Comparing Rankings
## Ranking the participants by their score, how many changed their positions? 

## How do participants who increased their ranking position compare to others w.r.t. their years of experience?

## How do participants who decreased their ranking position compare to others w.r.t. their years of experience?

## Are participants who increased, descreased, not changed ranking positions statistically significant distinct w.r.t. to score and years of experience?

# Comparing Correlation
## Years of programming and Score 
## Age and Score 
## Gender and Score

# References

