---
title: \vspace{3.5in}"Entropy Comparison between Adjusted and Original Qualification Score - Experiment-1"
author: "Christian Medeiros Adriano"
date: "`r Sys.Date()`"
bibliography: "..//..//bibtex//rmd_references.bib"
csl: "..//..//bibtex//acm-sig-proceedings.csl"
output:
   pdf_document:
      fig_caption: true
      number_sections: true
---
\newpage
\tableofcontents 
\listoffigures
\listoftables
\newpage 

    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library (entropy)

source("C://Users//Christian//Documents//GitHub//CausalModel_FaultUnderstanding//data_loaders//load_consent_create_indexes_E1.R")
df_consent <- load_consent_create_indexes();

```

# About this report

Compare the dispersion of the adjusted versus the original score. 

# Comparing Distributions


```{r density plots, echo=FALSE}

#Center (subtract the mean) but not Scales (divided by the standard deviation)
qualification_scores <- scale(df_consent$qualification_score, center=TRUE, scale=FALSE)
irt_scores <- scale(df_consent$adjusted_score, center=TRUE, scale=FALSE)

qualification_disc <- discretize(qualification_scores, numBins = 5)
irt_disc <- discretize(irt_scores,numBins = 5)


```

## How does the entropy (spread) of the distributions compare?

```{r compute entropy, echo=FALSE}
entropy(qualification_disc,method = "ML")
entropy(irt_disc,method = "ML")

entropy(qualification_disc,method = "Jeffreys")
entropy(irt_disc,method = "Jeffreys")

#Not Scaled
entropy(df_consent$qualification_score,method = "Jeffreys")
entropy(irt_scores,method = "Jeffreys")



```

Entropy reduced after adjustment, which was expected, because the adjusted score worked to rebalance the grades based on the difficulty of questions inferred by the number of people who got each question right.

## Comparative Entropy by Participant Group
Was the change in entropy more accentuated for certain groups of participants?

# Comparing Rankings
## Ranking the participants by their score, how many changed their positions? 

## How do participants who increased their ranking position compare to others w.r.t. their years of experience?

## How do participants who decreased their ranking position compare to others w.r.t. their years of experience?

## Are participants who increased, descreased, not changed ranking positions statistically significant distinct w.r.t. to score and years of experience?

# Comparing Correlation
## Years of programming and Score 
## Age and Score 
## Gender and Score

# References

